%------------------------
% MASTER RESUME
%
% >>> THIS IS SAMPLE DATA (Tony Stark / Iron Man) <<<
% It's here so you can see what a finished, filled-in master resume looks like.
% Open master_resume.pdf to view it.
%
% Run /start in Claude to REPLACE all of this with your own details, pulled from
% your LinkedIn profile and old resume, section by section. Nothing below is kept.
%
% The master is the single source of truth for every tailored resume.
% Structure reference: resume/master/resume_template.tex (do not redesign it).
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage[margin=0.5in, top=0.5in, bottom=0.5in]{geometry}

\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[xetex]{hyperref}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{fontspec}
% Picks the first font that exists on your machine, so this builds anywhere.
\IfFontExistsTF{Arial}{\setmainfont{Arial}}{%
  \IfFontExistsTF{Helvetica}{\setmainfont{Helvetica}}{%
    \IfFontExistsTF{TeX Gyre Heros}{\setmainfont{TeX Gyre Heros}}{%
      \setmainfont{Latin Modern Roman}}}}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\setstretch{1}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadingCompact}[3]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}, #2 & \textit{#3} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\vspace{-10pt}

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Tony Stark}} & Mobile: +1(310)5550100 \\
  Email: {tony@starkindustries.com} & Github:
  \href{https://github.com/tonystark}{github.com/tonystark}\\
  Location: Malibu, CA & LinkedIn: \href{https://www.linkedin.com/in/tonystark}{linkedin.com/in/tonystark}
\end{tabular*}
\vspace{-10pt}

% SUMMARY
\section{Summary}
Engineer and CEO of Stark Industries with 20+ years building advanced energy, propulsion, and AI systems. Designed the arc reactor and the Iron Man suit program. Founding member of the Avengers. MIT graduate in electrical engineering and physics.
\vspace{-10pt}

% EXPERIENCE
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheadingCompact{Stark Industries (CEO \& Chief Engineer)}{Malibu, CA}{05/08 - Present}
\vspace{-2pt}
\begin{itemize}[label=$\bullet$, leftmargin=8pt, itemsep=-1pt, topsep=2pt]
    \item Redirected the company from weapons manufacturing to clean energy, closing the weapons division and shipping an arc-reactor power platform within 12 months.
    \item Designed and built the arc reactor, a self-sustaining power source that runs the company campus and every suit in the program.
    \item Led R\&D for the Iron Man suit across 40+ iterations, improving flight ceiling, armor response time, and power efficiency each cycle.
    \item Built J.A.R.V.I.S., a natural-language AI that runs suit systems, lab automation, and diagnostics in real time.
    \item Grew Stark Industries clean-energy revenue to a market lead while holding 1000+ active patents in energy, materials, and propulsion.
\end{itemize}

\resumeSubheadingCompact{The Avengers (Founding Member)}{New York, NY}{05/12 - Present}
\vspace{-2pt}
\begin{itemize}[label=$\bullet$, leftmargin=8pt, itemsep=-1pt, topsep=2pt]
    \item Co-founded a response team for large-scale threats, leading hardware, aerial operations, and field communications.
    \item Designed and funded the team's compound, comms network, and rapid-deployment systems.
    \item Built and flew an autonomous suit fleet (the Iron Legion) for search, rescue, and containment.
\end{itemize}
\resumeSubHeadingListEnd
\vspace{-10pt}

% VOLUNTEER EXPERIENCE
\section{Volunteer Experience}
\resumeSubHeadingListStart
\resumeSubItem{Maria Stark Foundation}{Funded science education and research grants, including a full endowment for an MIT graduating class.}
\resumeSubItem{Stark Expo}{Revived a public expo for open scientific collaboration, hosting teams from industry and universities.}
\resumeSubHeadingListEnd
\vspace{-10pt}

% EDUCATION
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Massachusetts Institute of Technology}{Cambridge, MA}
    {B.S. Electrical Engineering and Physics, GPA: 4.00, summa cum laude}{09/87 - 05/91}
\resumeSubHeadingListEnd
\vspace{-10pt}

% PROJECTS
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Miniaturized Arc Reactor}{Built a palm-sized arc reactor delivering high sustained output from a portable core, powering the wearable suit.}
\resumeSubItem{Clean Energy Grid}{Prototyped a city-scale clean power grid running entirely on arc-reactor cells.}
\resumeSubHeadingListEnd
\vspace{-10pt}

% PUBLICATIONS
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{Self-Sustaining Arc Reactor Design}{Stark Industries technical white paper, 2010.}
\resumeSubItem{Applied Repulsor Physics}{Presented at the Stark Expo, 2010.}
\resumeSubHeadingListEnd
\vspace{-10pt}

% HONORS AND AWARDS
\section{Honors and Awards}
\resumeSubHeadingListStart
\resumeSubItem{Apogee Award for Industrial Innovation}{Awarded for advances in clean-energy engineering.}
\resumeSubItem{National Medal of Technology}{Recognized for contributions to energy and aerospace systems.}
\resumeSubHeadingListEnd
\vspace{-10pt}

% CERTIFICATIONS
\section{Certifications}
\resumeSubHeadingListStart
\resumeSubItem{FAA Commercial Pilot License}{Fixed-wing and experimental aircraft.}
\resumeSubHeadingListEnd
\vspace{-10pt}

% SKILLS SUMMARY
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Engineering \& Hardware}{Mechanical design, propulsion, materials science, nanotech, electronics, robotics}
\resumeSubItem{Software \& AI}{Natural-language AI, real-time control systems, Python, C++, embedded firmware}
\resumeSubItem{Leadership}{R\&D leadership, product strategy, fundraising, crisis operations}
\resumeSubHeadingListEnd

\end{document}
